Meeting Agenda with Domain Experts

### 2020-12-11 StateOfPractice/Methodology/Meeting Agenda with Domain Experts.tex
added modifiability experiment to meeting agenda with domain experts
added 2 tasks, and reordered tasks based on order of Methodology steps
cleaned up Meeting Agenda document

\subsection{Domain Analysis}
The domain analysis can be found in Section 3.2 of
\href{https://github.com/Ao99/MISEG/blob/master/docs/SRS/SRS.pdf}{SRS for
Medical Imaging Software} or
\href{https://github.com/peter-michalski/LatticeBoltzmannSolvers/blob/master/docs/SRS/CA.pdf}{CA
of Lattice Boltzmann Solvers}.

\subsection{Selecting Process}
The process of creating and shortening the list of software packages is
documented in
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Ao-Notes/Ao-Notes.pdf}{Ao's
Notes} or Peter's Notes \ad{TBD}

What do you think of our process of selecting software candidates?

@@

@@

\noindent Back to Section \ref{project_objectives}

@@

\noindent Back to Section \ref{research_questions}

\noindent Back to Section \ref{research_proposal}

@@

\noindent Back to Section \ref{top_10_list}

@@

\noindent Back to Section \ref{software_list}

\subsection{Review the Domain Analysis}
\pmi{added this task as requested in AIMSS issue  \href{https://github.com/smiths/AIMSS/issues/56}{56}}

\subsection{Review the AHP Ranking and Short List of Software Packages}
\pmi{added this task as requested in AIMSS issue  \href{https://github.com/smiths/AIMSS/issues/54}{54}}

\noindent Back to Section \ref{measurement_template}

\noindent Back to Section \ref{survey_short_list_projects}

\noindent Back to Section \ref{usability_tests}

>>>>

@@

\subsection{Modifiability Experiment}
\label{modifiability_experiment}
Presenter:

A brief introduction.

The usability test can be found..

Do you have any suggestions? Feedback can be provided later in Task
\ref{modifiability_experiment}

\subsection{Domain Analysis}
\label{domain_analysis}
The domain analysis can be found in Section 3.2 of
\href{https://github.com/Ao99/MISEG/blob/master/docs/SRS/SRS.pdf}{SRS for
Medical Imaging Software} or
\href{https://github.com/peter-michalski/LatticeBoltzmannSolvers/blob/master/docs/SRS/CA.pdf}{CA
of Lattice Boltzmann Solvers}.

\subsection{First AHP Ranking}
\label{first_AHP}
Presenter:

A brief introduction.

Do you have any feedback?

\subsection{Final AHP Ranking}
\label{final_AHP}
Presenter:

A brief introduction.

Do you have any feedback?

@@

\noindent Refer to Section \ref{project_objectives}

\noindent Refer to Section \ref{research_proposal}

@@

\noindent Refer to Section \ref{research_questions}

\noindent Refer to Section \ref{measurement_template}

\noindent Refer to Section \ref{survey_short_list_projects}

\noindent Refer to Section \ref{usability_tests}

\subsection{Review the Modifiability Experiment}
\label{task_modifiability_experiment}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\pmi{To be created}

\noindent Refer to Section \ref{modifiability_experiment}

@@

\noindent Refer to Section \ref{top_10_list}

@@

\noindent Refer to Section \ref{software_list}

\subsection{Review the Domain Analysis}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\pmi{To be created}

\noindent Refer to Section \ref{domain_analysis}

\subsection{Review the AHP Ranking and Short List of Software Packages}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\pmi{To be created}

\noindent Refer to Section \ref{first_AHP}

\subsection{Comment on Final Short List Ranking}
\label{task_final_ranking}
GitHub Issue:
\href{https://github.com/smiths/AIMSS/issues}{https://github.com/smiths/AIMSS/issues}
\pmi{To be created}

\noindent Refer to Section \ref{final_AHP}

%
%\section{Deleted Notes}
%\subsection{Selecting Process}
%The process of creating and shortening the list of software packages is
%documented in
%\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Ao-Notes/Ao-N%otes.pdf}{Ao's
%	Notes} or Peter's Notes \ad{TBD}
%
%What do you think of our process of selecting software candidates?
%
